\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-22 paper.tex
failure recovery

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{When an admitted demand finishes, it will be removed from $D_a$.} }\\
\hline
\multirow{3}{*}{$d=(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{for a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$D_a$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\subsection{Failure recovery} \label{backup}
In $\mathsf{BATE}$,  traffic can also be redistributed across the surviving tunnels via rerouting when any tunnel becomes unavailable.
%Previous tunnel-based traffic engineering schemes (such as FFC) keep link utilization low to prevent congestion when there are failures.
%Different from them, links have less vacant capacity under $\mathsf{BATE}$, therefore, when there are failures, re-routing might cause congestion.
%When a link $e'$ fails, all tunnels through this link  fails.
In reality, service providers have to derive refunding credits for violating availability targets (see $\S$\ref{background}).
$\mathsf{BATE}$ proactively considers failure scenarios and pre-computes backup allocation to maximize total revenue, and the surviving tunnels can be used immediately to support tenants.
%Each tunnel belongs to one flow pair.
%We can divide all node pairs into two groups, i.e.,  victim node pairs and normal node pairs, which is similar to \cite{sentinel}.
%Let $H$ denote all the victim node pairs when link $e'$ fails.
%Assume link $e'$ will fail, the normal tunnel set is $Q_{k}$ and the backup tunnel set is $Q'_{k}$.
%In reality, the backup tunnel set can be pre-computed by the network operators beforehand.
For example, Figure \ref{recovery} shows two services are from DC1 to DC4 and both of them need bandwidth demand of 2.
Link capacity is 1 everywhere.
Figure \ref{recovery}(a) shows the original traffic engineering allocation and it is used when no failures happen.
%if we assume the link between DC2 and DC4 is down, then DC1$\to$DC4 is victim node pair and DC1$\to$ DC2 is normal pair. 
%the backup tunnel set $Q'$=\{DC1$\to$DC2$\to$DC3$\to$DC4\} and normal tunnel set is 
%$Q$ =\{DC1$\to$DC3$\to$DC4\} for the victim node pair DC1$\to$DC4.
%Let $M_e$ denote the used bandwidth of link $e$ by normal node pairs,
Figure \ref{recovery}(b) depicts the backup allocation result when we assume the link between DC2 and DC4 is down, and the result will be put into practice when link DC2 $\to$ DC4 failure is detected.
Network scenario number is huge for large-scale network and we assume that at any time, only one link in the network could fail. 
If we assume network scenario $ \bm{z}$ could happen, and let $f^{\bm{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \bm{z}}_k$, where $T^ { \bm{z}}_k$ is the surviving tunnel set under scenario $ \bm{z}$ and it should be non-negative, i.e.,
\begin{equation}
f^{\bm{z}}_{ikt} \ge 0, \quad\forall d \in D ,  k\in K,   t\in T^{\bm{z}}_k.
\label{constraint-f3}
\end{equation}

@@

\begin{small}
\begin{eqnarray} \label{B-constraint}
\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in T^{ \bm{z}}_k} f^{ \bm{z}}_{ikt}u_t^e \le c_e \times A_e^{ \bm{z}}
\end{eqnarray}
\end{small}

The revenue return for $i$ over node pair $k$ can be described:
\begin{small}
\begin{eqnarray} \label{B-return}
R_{ik}=\frac{\sum_{t\in T^{ \bm{z}}_k} f^{ \bm{z}}_{ikt}}{\mathbf{b}^k_d}, \forall  d \in D_a,  k \in K
\end{eqnarray}
\end{small}

If the allocated bandwidth  of $i\in I_a$ between each node pair is larger than its need (i.e., $R_{ik} \ge 1, \forall i \in  I_a$), the profit unit is 1, 
%If it is between $\beta_j^{k}$ and $\beta_j^{k+1}$, then the profit is $\alpha_j^k$, where $1>\alpha_j^1>\alpha_j^2>...>\alpha_j^k$.
otherwise, there is a penalty, which can be derived from SLA and we use $\mu_{\gamma_i}$ to denote its penalty.
Then, the profit of $i$ is:

\begin{equation}
\forall  d \in D_a : h_i=
\begin{cases}
1 &\text{$\forall k \in K: R_{ik} \ge 1 $}\\
\mu_{\gamma_i} &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation}

@@

\begin{equation}
\begin{cases}
h_i=y_i+\mu_{\gamma_i}*(1-y_i),&{\forall d \in D_a.} \\
R_{ik} < M*y_i+1-y_i,&{\forall d \in D_a,  k\in K.} \\
R_{ik} >= y_i,&{\forall d \in D_a,  k\in K.} \\
y_i \in\{0,1\},&{\forall d \in D_a.} \\
\end{cases}
\label{A-SSS2}
\end{equation}

Where $M$ is a big integer that is at least larger than the upper bound of $R_{ik}$.
Let $w_i$ denote the profit of demand $i$ when its availability target can be satisfied.
The goal of failure recovery is to maximize profits of all the admitted demands, and we can give the problem formulation finally:

\begin{equation}
\small
\begin{aligned} \label{BATE-recovery}
 &maximize  \sum_{i\in I_a} w_i\times h_i\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t.  (\ref{constraint-f3}), (\ref{B-constraint}), (\ref{B-return}), (\ref{A-SSS2})
\end{array}
\end{aligned}
\end{equation}

The auxiliary output variables $y_i$ are chosen from \{0,1\},  so that the  failure recovery problem is a 0-1 Mixed-integer linear programming.

>>>>

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{When an admitted demand finishes, it will be removed from $D_a$.} }\\
\hline
\multirow{3}{*}{$d=(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{for a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$D_a$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\subsection{Failure recovery} \label{backup}
In $\mathsf{BATE}$,  traffic can also be redistributed across the surviving tunnels via rerouting when any tunnel becomes unavailable.
%Previous tunnel-based traffic engineering schemes (such as FFC) keep link utilization low to prevent congestion when there are failures.
%Different from them, links have less vacant capacity under $\mathsf{BATE}$, therefore, when there are failures, re-routing might cause congestion.
%When a link $e'$ fails, all tunnels through this link  fails.
In reality, service providers have to derive refunding credits for violating availability targets (see $\S$\ref{background}).
$\mathsf{BATE}$ proactively considers failure scenarios and pre-computes backup allocation to maximize total revenue, and the surviving tunnels can be used immediately to support tenants.
%Each tunnel belongs to one flow pair.
%We can divide all node pairs into two groups, i.e.,  victim node pairs and normal node pairs, which is similar to \cite{sentinel}.
%Let $H$ denote all the victim node pairs when link $e'$ fails.
%Assume link $e'$ will fail, the normal tunnel set is $Q_{k}$ and the backup tunnel set is $Q'_{k}$.
%In reality, the backup tunnel set can be pre-computed by the network operators beforehand.
For example, Figure \ref{recovery} shows two services are from DC1 to DC4 and both of them need bandwidth demand of 2.
Link capacity is 1 everywhere.
Figure \ref{recovery}(a) shows the original traffic engineering allocation and it is used when no failures happen.
%if we assume the link between DC2 and DC4 is down, then DC1$\to$DC4 is victim node pair and DC1$\to$ DC2 is normal pair. 
%the backup tunnel set $Q'$=\{DC1$\to$DC2$\to$DC3$\to$DC4\} and normal tunnel set is 
%$Q$ =\{DC1$\to$DC3$\to$DC4\} for the victim node pair DC1$\to$DC4.
%Let $M_e$ denote the used bandwidth of link $e$ by normal node pairs,
Figure \ref{recovery}(b) depicts the backup allocation result when we assume the link between DC2 and DC4 is down, and the result will be put into practice when link DC2 $\to$ DC4 failure is detected.
Network scenario number is huge for large-scale network and we assume that at any time, only one link in the network could fail. 
If we assume network scenario $ \bm{z}$ could happen, and let 
%$f^{\bm{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \bm{z}}_k$, where 
$T^ { \bm{z}}_k$ denote the surviving tunnel set under scenario $ \bm{z}$ and the bandwidth allocated for demand $d$ over tunnel $t$ should be non-negative, i.e.,
\begin{equation}
f^{t}_{d} \ge 0, \quad\forall d \in D ,  k\in K : t\in T^{\bm{z}}_k.
\label{constraint-f3}
\end{equation}

@@

\begin{small}
\begin{eqnarray} \label{B-constraint}
\sum_{d\in D_a}\sum_{k\in K:t\in T^{ \bm{z}}_k} f^{t}_{d}u_t^e \le c_e \times A_e^{ \bm{z}}
\end{eqnarray}
\end{small}

The revenue return for $i$ over node pair $k$ can be described:
\begin{small}
\begin{eqnarray} \label{B-return}
R_{dk}=\frac{\sum_{t\in T^{ \bm{z}}_k} f^{t}_{d}}{\mathbf{b}^k_d}, \forall  d \in D_a,  k \in K
\end{eqnarray}
\end{small}

If the allocated bandwidth  of BA demand $d$ between each node pair is larger than its need (i.e., $R_{dk} \ge 1, \forall d \in  D_a$), the profit unit is 1, 
%If it is between $\beta_j^{k}$ and $\beta_j^{k+1}$, then the profit is $\alpha_j^k$, where $1>\alpha_j^1>\alpha_j^2>...>\alpha_j^k$.
otherwise, there is a penalty, which can be derived from SLA and we use $\mu_{d}$ to denote its penalty.
Then, the profit of $d$ is:

\begin{equation}
\forall  d \in D_a : h_d=
\begin{cases}
1 &\text{$\forall k \in K: R_{dk} \ge 1 $}\\
\mu_{d} &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation}

@@

\begin{equation}
\begin{cases}
h_d=y_d+\mu_{d}*(1-y_d),&{\forall d \in D_a.} \\
R_{dk} < M*y_d+1-y_d,&{\forall d \in D_a,  k\in K.} \\
R_{dk} >= y_d,&{\forall d \in D_a,  k\in K.} \\
y_d \in\{0,1\},&{\forall d \in D_a.} \\
\end{cases}
\label{A-SSS2}
\end{equation}

Where $M$ is a big integer that is at least larger than the upper bound of $R_{dk}$.
Let $w_d$ denote the profit of demand $d$ when its availability target can be satisfied.
The goal of failure recovery is to maximize profits of all the admitted demands, and we can give the problem formulation finally:

\begin{equation}
\small
\begin{aligned} \label{BATE-recovery}
 &maximize  \sum_{d\in D_a} w_d\times h_d\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t.  (\ref{constraint-f3}), (\ref{B-constraint}), (\ref{B-return}), (\ref{A-SSS2})
\end{array}
\end{aligned}
\end{equation}

The auxiliary output variables $y_d$ are chosen from \{0,1\},  so that the  failure recovery problem is a 0-1 Mixed-integer linear programming.
